---
title: "Pro-sepsis"
#author: "Nartlada Chantharojwong & Vorapathu Thaineua"
date: "Compiled on `r format(Sys.time(), '%B %d, %Y - %H:%M')`"
output:
  html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  cache = FALSE
)

library(tidyverse)
library(haven)      # Read SAS dataset
library(purrr)      # Apply function (sum) to each element 
library(scales)     # Format numeric values
library(DiagrammeR) # Create flowchart
library(gtsummary)  # Create publication-ready summary tables 
library(survival)   # Survival analysis
library(gt)         # Format gtsummary output

theme_gtsummary_compact(font_size = 10)
# theme_gtsummary_journal("lancet")
```

```{r functions}
# Format gtsummary outputs
format_table <- function(t, grp = "") {

  # Hide p-values of SIRSqSOFA, SIRS, and QSofa in table 1
  if (deparse(substitute(t)) == 't1') {
    t <- t %>% add_p(include = -c('SIRSqSOFA', 'SIRS', 'QSofa'))
  } else {
    t <- t %>% add_p()
  }
  
  t <- t %>%
    bold_p(t = 0.05) %>%                         # Bold p-value if significant
    add_overall() %>%                            # Add overall column
    modify_spanning_header(c("stat_1", "stat_2") ~ "**Mortality Outcome**") %>%
    # Empty stub head label and split header line
    modify_header(                     
      update = list(
        label ~ "",
        all_stat_cols(stat_0 = FALSE) ~ "**{level}**<br>N = {n}",
        stat_0 ~ "**Overall**<br>N = {N}"
      )
    ) %>%
    # Convert to gt and use default left align
    as_gt(include = -cols_align) %>%
    # Standard column width to fit every table
    cols_width(label ~ px(230),
               p.value ~ px(60),
               everything() ~ px(100)) %>%
    # Add footnote about pending cases
    tab_footnote(
      footnote = str_glue(n_miss, " cases are pending for final outcome"),
      locations = cells_column_labels(columns = "stat_0")
    )

  # Add a row group for 'check all that apply' variables
  if (grp != "") {
    t <- t %>%
      tab_row_group(group = grp,
                    rows = everything()) %>%
      tab_style(style = cell_text(weight = "bold"),
                locations = cells_row_groups(groups = everything()))
  }
  
  return(t)
  
}

# Sort dichotomous variables by descending frequency
sort_var <- function(...) {
  
  df_enr %>%
    filter(!is.na(dead)) %>% 
    select(...) %>%
    map_dbl(sum, na.rm = TRUE) %>%
    sort(decreasing = TRUE)
  
}
```

```{r data}
# Screening
df_scr <-
  read_sas(
    "C:/Projects/ProSepsis/SAS/MF/tblPart1.sas7bdat",
    "C:/Projects/ProSepsis/SAS/MF/prosepsis.sas7bcat"
  )

# Enrollment
df_enr <-
  read_sas(
    "C:/Projects/ProSepsis/SAS/MF/psmast.sas7bdat",
    "C:/Projects/ProSepsis/SAS/MF/prosepsis.sas7bcat"
  ) %>%
  mutate(
    dead = factor(
      dead,
      levels = c(1, 2),
      labels = c('Dead', 'Alive')
    ),
    across(
      c(
        Sex,
        PlaceChk_n,
        Occupation,
        OPD_IPD,
        Sepsis_Scale,
        HIV,
        Covid21,
        DischargeStatus,
        DischargeType,
        OPDOutcome,
        Outcome28Days
      ),
      ~ as_factor(.)
    ),
    across(
      c(
        Refer,
        SIRS,
        QSofa,
        UnSmoke:UnAlcohol,
        NP,
        CB,
        Sofa_Sepsis,
        HBsAgr,
        HBc,
        AntiHBs,
        AntiHCV,
        Influenza,
        Leptor,
        MalariaR,
        Melio,
        RSV
      ),
      ~ ifelse(. == 2, 0, .)
    )
  )

n_enr  = nrow(df_enr)
n_miss = sum(is.na(df_enr$dead), na.rm = TRUE)
```

<br><br> **Figure 1**: Flow chart presenting the number of screening and enroll patients with sepsis who participating in this sepsis epidemiology activities

<center>

```{r flowchart}
source("flowchart.R", local = knitr::knit_global())
d
```

</center>

<br>

\newpage

**Table 1**: Descriptive statistical analysis of the baseline demographic data and clinical characteristics of the enrolled suspected sepsis cases at Nakhon Phanom and Mae Sot hospitals during November 2021- July 8, 2022 (N=`r n_enr`)

```{r t1}
t1 <- df_enr %>%
  mutate(
    SIRSqSOFA = ifelse(Group == 1, 1, 0)
  ) %>% 
  select(
    dead,
    Age_year,
    Sex,
    PlaceChk_n,
    Occupation,
    Refer,
    OPD_IPD,
    SIRS,
    QSofa,
    SIRSqSOFA,
    Sepsis_Scale
  ) %>%
  tbl_summary(
    by = dead,
    label = list(
      Age_year     ~ 'Age',
      PlaceChk_n   ~ 'Admission ward',
      Refer        ~ 'Transferred',
      OPD_IPD      ~ 'Patient admission as',
      SIRS         ~ '(Any) SIRS >= 2 scores',
      QSofa        ~ '(Any) qSOFA >= 2 scores',
      SIRSqSOFA    ~ '(Any) SIRS and qSOFA >= 2 scores',
      Sepsis_Scale ~ 'Sepsis determination (SOFA)'
    ),
    digits = Age_year ~ 1,
    missing = "no",
    sort = list(Occupation ~ "frequency")
  ) %>%
  bold_labels() %>%
  # Add labels describing stat for each variable
  add_stat_label()
t1 <- format_table(t1)
t1
```

<br>

\newpage

```{r t1_cc}
vars <- names(sort_var(CCFever:CCJointPain))
t1_cc <- df_enr %>%
  zap_labels() %>% 
  select(dead, vars, CCOther) %>%
  tbl_summary(by = dead) %>% 
  format_table("Chief Complaint")
t1_cc
```

<br>

```{r t1_if}
vars <- names(sort_var(IFTropSep:IFNerve))
t1_if <- df_enr %>%
  zap_labels() %>% 
  select(dead, vars, IFOth) %>%
  tbl_summary(
    by = dead,
    label = list(
      IFTropSep     ~ 'Tropical infection',
      IFRespiratory ~ 'Respiratory',
      IFBlood       ~ 'Blood',
      IFGas         ~ 'Gastrointestinal track',
      IFUrine       ~ 'Urinary',
      IFSkin        ~ 'Skin/Soft tissue/bone',
      IFNerve       ~ 'Central nervous system',
      IFOth         ~ 'Others'
    )
  ) %>%
  format_table("Source of Infection")
t1_if
```

<br>

\newpage

**Table 2**: Clinical information and laboratory result of enrolled suspected sepsis cases participating at Nakhon Phanom and Mae Sot hospitals during November 2021- July 8, 2022 (N=`r n_enr`)

```{r t2_un}
vars <- names(sort_var(UnDiabetes:UnThalassemia))
t2_un <- df_enr %>%
  zap_labels() %>% 
  select(dead, vars, UnOth) %>%
  tbl_summary(by = dead) %>%
  format_table("Underlying Condition/Co-morbidity")
t2_un
```

<br>

```{r t2_risk}
vars <- names(sort_var(UnSmoke:UnAlcohol))
t2_risk <- df_enr %>%
  select(dead, vars, HIV, Covid21) %>%
  tbl_summary(
    by = dead,
    label = list(UnSmoke   ~ 'Smoking',
                 UnAlcohol ~ 'Alcohol'),
    missing = "no"
  ) %>%
  format_table("Risk Behavior")
t2_risk
```

<br>

```{r t2_pui}
t2_pui <- df_enr %>%
  select(dead, NP, CB) %>%
  tbl_summary(by = dead,
              missing = "no") %>%
  format_table("PUI (SARS-CoV2 NGS and TAC)")
t2_pui
```

<br>

```{r t2_dx}
vars <- names(sort_var(DxFever:DxMening))
t2_dx <- df_enr %>%
  zap_labels() %>% 
  select(dead, vars, DxOther) %>%
  tbl_summary(by = dead) %>%
  format_table("Provisional Diagnosis")
t2_dx
```

<br>

```{r t2_or}
t2_or <- df_enr %>%
  mutate(
    across(SOFA1:SOFA6, ~ ifelse(. > 1, 1, .))
  ) %>% 
  select(dead, SOFA1:SOFA6, Sofa_Sepsis) %>%
  tbl_summary(
    by = dead,
    label = list(
      SOFA1       ~ 'RS (PaO2/Fio2 <400 or infiltration on CXR)',
      SOFA2       ~ 'Liver (Bilirubin > 1.2 mg/dl)',
      SOFA3       ~ 'Cardiovascular (MAP <70 mmHg)',
      SOFA4       ~ 'CNS (Glasgow Coma Scale <15)',
      SOFA5       ~ 'Blood (Platelet < 150×103/μl)',
      SOFA6       ~ 'Renal (Cr.>1.2 mg/dl)',
      Sofa_Sepsis ~ 'SOFA score (SOFA_Total2) >= 2'
    ),
    missing = "no"
  ) %>%
  format_table("Organ Dysfunction")
t2_or
```

<br>

```{r t2_cul_s}
t2_cul_s <- df_enr %>%
  zap_labels() %>% 
  select(dead, CulBlood_ever:CulOther_ever) %>%
  tbl_summary(
    by = dead,
    label = list(
      CulBlood_ever  ~ 'Blood',
      CulSputum_ever ~ 'Sputum',
      CulUrine_ever  ~ 'Urine',
      CulCSF_ever    ~ 'CSF',
      CulOther_ever  ~ 'Others'
    )
  ) %>%
  format_table("Microbiology: Culture Source")
t2_cul_s
```

<br>

\newpage

```{r t2_rdt}
df_enr$covid19_r <- ifelse(grepl('1', df_enr$Covid_tests, fixed = TRUE), 1, 0)
df_enr$dengue_r  <- ifelse(grepl('1', df_enr$Dengue_tests, fixed = TRUE), 1, 0)
df_enr$denguel_r <- ifelse(grepl('1', df_enr$DengueL_tests, fixed = TRUE), 1, 0)
df_enr$hbshcv_r  <- ifelse(grepl('1', df_enr$HBSHCV_tests, fixed = TRUE), 1, 0)
df_enr$scrubt_r  <- ifelse(grepl('1', df_enr$ScrubT_tests, fixed = TRUE), 1, 0)
vars <-
  names(
    sort_var(
      covid19_r:denguel_r,
      HBsAgr,
      HBc,
      AntiHBs,
      AntiHCV,
      hbshcv_r,
      Influenza,
      Leptor,
      MalariaR,
      Melio,
      scrubt_r,
      RSV
    )
  )
t2_rdt <- df_enr %>%
  select(dead, vars) %>%
  tbl_summary(
    by = dead,
    label = list(
      covid19_r ~ 'COVID-19 +',
      dengue_r  ~ 'Dengue +',
      denguel_r ~ 'Dengue + (lab)',
      HBsAgr    ~ 'HBsAg +',
      HBc       ~ 'HBc +',
      AntiHBs   ~ 'Anti-HBs +',
      AntiHCV   ~ 'Anti-HCV +',
      hbshcv_r  ~ 'Anti-HBs/Anti-HCV +',
      Influenza ~ 'Influenza +',
      Leptor    ~ 'Leptospirosis +',
      MalariaR  ~ 'Malaria +',
      Melio     ~ 'Melioidosis +',
      scrubt_r  ~ 'Scrub typhus +',
      RSV       ~ 'RSV +'
    ),
    missing = "no"
  ) %>%
  format_table("RDT")
t2_rdt
```

<br>

```{r t2_trt}
vars <- names(sort_var(penicillin_ever:parasitedrug_ever))
t2_trt <- df_enr %>%
  zap_labels() %>% 
  select(dead, vars, otheranti_ever) %>%
  tbl_summary(
    by = dead,
    label = list(
      penicillin_ever   ~ 'Penicillin',
      cephalG1_ever     ~ 'Cephalosporin 1st',
      cephalG2_ever     ~ 'Cephalosporin 2nd',
      cephalG3_ever     ~ 'Cephalosporin 3rd',
      cephalG4_ever     ~ 'Cephalosporin 4th',
      macroclide_ever   ~ 'Macrolide',
      tetra_ever        ~ 'Tetracycline',
      quinolone_ever    ~ 'Quinolone',
      amino_ever        ~ 'Aminoglycoside',
      sulfon_ever       ~ 'Sulfonamide',
      carbapenem_ever   ~ 'Carbapenem',
      lincomycin_ever   ~ 'Lincomycin',
      polypep_ever      ~ 'Polypep',
      vancomycin_ever   ~ 'Vancomycin',
      tbdrug_ever       ~ 'TB drugs',
      antifungal_ever   ~ 'Antifungal',
      antiviral_ever    ~ 'Antiviral',
      antimalaria_ever  ~ 'Antimalarial',
      parasitedrug_ever ~ 'Parasite drugs',
      otheranti_ever    ~ 'Others'
    ),
    missing = "no"
  ) %>%
  format_table("Treatment Received")
t2_trt
```

<br>

\newpage

**Table 4**: Bivariate analysis discharge outcome of patient with sepsis activities at Nakhon Phanom and Mae Sot hospitals during November 2021- July 8, 2022 (N=`r n_enr`)

```{r t4_dx}
vars <- names(sort_var(Pneumonia:Malaria))
t4_dx <- df_enr %>%
  zap_labels() %>%
  mutate(
    across(Principal1:Principal3, ~ na_if(., "")),
    Others = ifelse(!is.na(Principal1) | !is.na(Principal2) | !is.na(Principal3),
                    1,
                    0)
  ) %>%
  select(dead, vars, Others) %>%
  tbl_summary(by = dead,
              missing = "no") %>%
  format_table("Principal Diagnosis")
t4_dx
```

<br>

```{r t4}
t4 <- df_enr %>%
  select(dead,
         DischargeStatus,
         DischargeType,
         OPDOutcome,
         Outcome28Days) %>%
  tbl_summary(
    by = dead,
    label = list(
      DischargeStatus ~ 'Discharge status (IDP only)',
      DischargeType   ~ 'Discharge type (IDP only)',
      OPDOutcome      ~ 'Treatment outcome after 28 OPD admission (OPD only)',
      Outcome28Days   ~ 'Treatment outcome after 28 days (FU by phone)'
    ),
    missing = "no"
  ) %>%
  bold_labels() %>%
  format_table()
t4
```

```{r}
# uni <- df_enr %>%
#   select(Age_year, Sex, Refer, Sepsis:Cancer, Liver, TotalCharge, dead, stime) %>%
#   mutate(dead = ifelse(dead == 0, 2, dead)) %>%
#   tbl_uvregression(method = coxph,
#                    y = Surv(stime, dead),
#                    exponentiate = TRUE) %>%
#   add_global_p()
# uni
```
