---
title: "Pro-sepsis"
#author: "Nartlada Chantharojwong & Vorapathu Thaineua"
date: "Compiled on `r format(Sys.time(), '%B %d, %Y - %H:%M')`"
output:
  html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  cache = FALSE
)

library(tidyverse)
library(haven)      # Read SAS dataset
library(purrr)      # Apply function (sum) to each element
library(scales)     # Format numeric values
library(labelled)   # Set organism variable labels
library(DiagrammeR) # Create flowchart
library(gtsummary)  # Create publication-ready summary tables
library(survival)   # Survival analysis
library(gt)         # Format gtsummary output

theme_gtsummary_compact(font_size = 10)
```

```{r functions}
# Format gtsummary outputs before merging
format_table_1 <- function(t, overall)  {

  # Hide p-values of SIRSqSOFA, SIRS, and QSofa in table 1
  if (deparse(substitute(t)) == 't1') {
    t <- add_p(t, include = -c('SIRSqSOFA', 'SIRS', 'QSofa'))
  } else {
    t <- add_p(t, test.args = all_tests("fisher.test") ~ list(workspace = 2e9))
  }

  # Bold p-value if significant
  t <- bold_p(t, t = 0.05)

  # Add overall column if overall = TRUE
  if (overall == TRUE) {
    t <- t %>%
      add_overall() %>%
      # Empty stub head label and split header line
      modify_header(
        update = list(
          label ~ "",
          all_stat_cols(stat_0 = FALSE) ~ "**{level}**<br>N = {n}",
          stat_0 ~ "**Overall**<br>N = {N}"
        )
      )
  } else {
    t <- t %>%
      # Empty stub head label and split header line
      modify_header(
        update = list(
          label ~ "",
          all_stat_cols() ~ "**{level}**<br>N = {n}"
        )
      )
  }

  modify_footnote(t, starts_with('stat') ~ NA)

}

# Format gtsummary outputs after merging
format_table_2 <- function(t) {

  gt <- t %>%
    # Convert to gt and use default left align
    as_gt() %>%
    # Standard column width to fit every table
    cols_width(
      label ~ px(230),
      stat_0_1 ~ px(100),
      starts_with('p.value') ~ px(50),
      everything() ~ px(70)
    ) %>%
    tab_style(style = cell_text(weight = "bold"),
              locations = cells_row_groups()) %>%
    tab_style(style = cell_text(weight = "bold"),
              locations = cells_body(columns = label,
                                     rows = variable %in% c("gramneg","grampos"))) %>%
        tab_style(style = cell_text(weight = "bold"),
              locations = cells_body(columns = label,
                                     rows = variable %in% c("OxyInbu","vasopressor","oxygensupp","Hypoglycemia"))) %>%
    tab_options(
      row_group.border.top.width = 1,
      row_group.border.bottom.width = 1,
      table.border.bottom.style = "hidden"
    )

  if (deparse(substitute(t)) != 't3b') {
    # Add footnote about pending cases
    gt <- tab_footnote(
      gt,
      footnote = str_glue(n_miss, " cases are pending for final outcome"),
      locations = cells_column_labels(columns = "stat_0_1")
    )
  }
  
  return(gt)
  
}

# Sort dichotomous variables by descending frequency
sort_var <- function(df, ...) {

    df %>%
    filter(!is.na(dead28c)) %>%
    select(...) %>%
    map_dbl(sum, na.rm = TRUE) %>%
    sort(decreasing = TRUE)

}

create_t1 <- function(df, overall = FALSE) {
  t1 <- df %>%
    mutate(SIRSqSOFA = ifelse(Group == 1, 1, 0),
           Age_gp4 = cut(
      Age_year,
      breaks = c(0, 14, 44,64 ,Inf),
      labels = c('<15','15-44','45-64','>64'))) %>% 
    select(
      dead28c,
      Age_year,
      Age_gp4,
      BMIgp,
      Sex,
      PlaceChk_n,
      Occupation,
      Refer,
      SIRS,
      QSofa,
      SIRSqSOFA,
      Sepsis_Scale
    ) %>%
    tbl_summary(
      by = dead28c,
      label = list(
        Age_year     ~ 'Age',
        Age_gp4   ~ 'Age group',
        BMIgp  ~ 'BMI range ',
        PlaceChk_n   ~ 'Admission ward',
        Refer        ~ 'Transferred',
        SIRS         ~ '(Any) SIRS >= 2 scores',
        QSofa        ~ '(Any) qSOFA >= 2 scores',
        SIRSqSOFA    ~ '(Any) SIRS and qSOFA >= 2 scores',
        Sepsis_Scale ~ 'Sepsis determination (SOFA)'
      ),
      missing = "no",
      sort = list(Occupation ~ "frequency")
    ) %>%
    bold_labels() %>%
    # Add labels describing stat for each variable
    add_stat_label()
  t1 <- format_table_1(t1, overall)
}

create_t1_cc <- function(df, overall = FALSE) {
  vars <- names(sort_var(df, CCFever:CCJointPain))
  df %>%
    zap_labels() %>%
    select(dead28c, vars, CCOther) %>%
    tbl_summary(by = dead28c) %>%
    format_table_1(overall)
}

create_t1_if <- function(df, overall = FALSE) {
  vars <- names(sort_var(df, IFTropSep:IFNerve))
  df %>%
    zap_labels() %>%
    select(dead28c, vars, IFOth) %>%
    tbl_summary(
      by = dead28c,
      label = list(
        IFTropSep     ~ 'Tropical infection',
        IFRespiratory ~ 'Respiratory',
        IFBlood       ~ 'Blood',
        IFGas         ~ 'Gastrointestinal track',
        IFUrine       ~ 'Urinary',
        IFSkin        ~ 'Skin/Soft tissue/bone',
        IFNerve       ~ 'Central nervous system',
        IFOth         ~ 'Others'
      )
    ) %>%
    format_table_1(overall)
}

create_t2_un <- function(df, overall = FALSE) {
  vars <- names(sort_var(df, UnDiabetes:UnThalassemia))
  df %>%
    zap_labels() %>%
    select(dead28c, vars, UnOth) %>%
    tbl_summary(by = dead28c) %>%
    format_table_1(overall)
}

create_t2_risk <- function(df, overall = FALSE) {
  vars <- names(sort_var(df, UnSmoke:UnAlcohol))
  df %>%
    select(dead28c, vars, HIV, Covid21) %>%
    tbl_summary(
      by = dead28c,
      label = list(UnSmoke   ~ 'Smoking',
                   UnAlcohol ~ 'Alcohol'),
      missing = "no"
    ) %>%
    format_table_1(overall)
}

create_t2_pui <- function(df, overall = FALSE) {
  df %>%
    select(dead28c, NP, CB) %>%
    tbl_summary(by = dead28c,
                missing = "no") %>%
    format_table_1(overall)
}

create_t2_dx <- function(df, overall = FALSE) {
  vars <- names(sort_var(df, DxFever:DxMening))
  df %>%
    zap_labels() %>%
    select(dead28c, vars, DxOther) %>%
    tbl_summary(by = dead28c) %>%
    format_table_1(overall)
}

create_t2 <- function(df, overall = FALSE) {
  df %>%
   zap_labels() %>%
    select(dead28c, OxyInbu,vasopressor,oxygensupp,Hypoglycemia) %>%
    tbl_summary(
      by = dead28c,
      label = list(
        OxyInbu ~ 'Ventilator use',
        vasopressor ~ 'Vasopressor use',
        oxygensupp ~ 'Supplement Oxygen',
        Hypoglycemia ~ 'Hypoglycemia '
      ),
      missing = "no"
    ) %>%
    format_table_1(overall)
}


create_t2_or <- function(df, overall = FALSE) {
  df %>%
    mutate(across(SOFA2:SOFA6, ~ ifelse(. > 1, 1, .)),
           SOFA1 = ifelse(SOFA1==3,1,0)) %>%
    select(dead28c, SOFA1:SOFA6, Sofa_Sepsis) %>%
    tbl_summary(
      by = dead28c,
      label = list(
        SOFA1       ~ 'RS (PaO2/Fio2 >=100 and < 200 with respiratory support',
        SOFA2       ~ 'Liver (Bilirubin > 1.2 mg/dl)',
        SOFA3       ~ 'Cardiovascular (MAP <70 mmHg)',
        SOFA4       ~ 'CNS (Glasgow Coma Scale <15)',
        SOFA5       ~ 'Blood (Platelet < 150×103/μl)',
        SOFA6       ~ 'Renal (Cr.>1.2 mg/dl)',
        Sofa_Sepsis ~ 'SOFA score (SOFA_Total2) >= 2'
      ),
      missing = "no"
    ) %>%
    format_table_1(overall)
}

create_t2_cul_s <- function(df, overall = FALSE) {
  df %>%
    zap_labels() %>%
    select(dead28c, CulBlood_ever:CulOther_ever) %>%
    tbl_summary(
      by = dead28c,
      label = list(
        CulBlood_ever  ~ 'Blood',
        CulSputum_ever ~ 'Sputum',
        CulUrine_ever  ~ 'Urine',
        CulCSF_ever    ~ 'CSF',
        CulOther_ever  ~ 'Others'
      )
    ) %>%
    format_table_1(overall)
}

create_t2_rdt <- function(df, overall = FALSE) {
  vars <-
    names(
      sort_var(
        df,
        covid19_r:denguel_r,
        HBsAgr,
        HBc,
        AntiHBs,
        AntiHCV,
        hbshcv_r,
        Influenza,
        Leptor,
        MalariaR,
        Melio,
        scrubt_r,
        RSV
      )
    )
  df %>%
    select(dead28c, vars) %>%
    tbl_summary(
      by = dead28c,
      label = list(
        covid19_r ~ 'COVID-19 +',
        dengue_r  ~ 'Dengue +',
        denguel_r ~ 'Dengue + (lab)',
        HBsAgr    ~ 'HBsAg +',
        HBc       ~ 'HBc +',
        AntiHBs   ~ 'Anti-HBs +',
        AntiHCV   ~ 'Anti-HCV +',
        hbshcv_r  ~ 'Anti-HBs/Anti-HCV +',
        Influenza ~ 'Influenza +',
        Leptor    ~ 'Leptospirosis +',
        MalariaR  ~ 'Malaria +',
        Melio     ~ 'Melioidosis +',
        scrubt_r  ~ 'Scrub typhus +',
        RSV       ~ 'RSV +'
      ),
      missing = "no"
    ) %>%
    format_table_1(overall)
}

create_t2_trt <- function(df, overall = FALSE) {
  vars <- names(sort_var(df, penicillin_ever:parasitedrug_ever))
  df %>%
    zap_labels() %>%
    select(dead28c, vars, otheranti_ever) %>%
    tbl_summary(
      by = dead28c,
      label = list(
        penicillin_ever   ~ 'Penicillin',
        cephalG1_ever     ~ 'Cephalosporin 1st',
        cephalG2_ever     ~ 'Cephalosporin 2nd',
        cephalG3_ever     ~ 'Cephalosporin 3rd',
        cephalG4_ever     ~ 'Cephalosporin 4th',
        macroclide_ever   ~ 'Macrolide',
        tetra_ever        ~ 'Tetracycline',
        quinolone_ever    ~ 'Quinolone',
        amino_ever        ~ 'Aminoglycoside',
        sulfon_ever       ~ 'Sulfonamide',
        carbapenem_ever   ~ 'Carbapenem',
        lincomycin_ever   ~ 'Lincomycin',
        polypep_ever      ~ 'Polypep',
        vancomycin_ever   ~ 'Vancomycin',
        tbdrug_ever       ~ 'TB drugs',
        antifungal_ever   ~ 'Antifungal',
        antiviral_ever    ~ 'Antiviral',
        antimalaria_ever  ~ 'Antimalarial',
        parasitedrug_ever ~ 'Parasite drugs',
        otheranti_ever    ~ 'Others'
      ),
      missing = "no"
    ) %>%
    format_table_1(overall)
}

create_t3 <- function(df, outcome = dead28c, overall = FALSE) {
  outcome = enquo(outcome)
  varsneg <- names(sort_var(df, achromobacter:vibrio))
  varspos <- names(sort_var(df, dermacoccus:streptococcus_su))
  df %>%
    zap_labels() %>%
    select(!!outcome, gramneg, varsneg, grampos, varspos) %>%
    tbl_summary(by = !!outcome) %>%
    format_table_1(overall)
}

create_t4_dx <- function(df, overall = FALSE) {
  vars <- names(sort_var(df, Pneumonia:Malaria))
  df %>%
    zap_labels() %>%
    mutate(across(Principal1:Principal3, ~ na_if(., "")),
           Others = ifelse(
             !is.na(Principal1) | !is.na(Principal2) | !is.na(Principal3),
             1,
             0
           )) %>%
    select(dead28c, vars, Others) %>%
    tbl_summary(by = dead28c,
                missing = "no") %>%
    format_table_1(overall)
}

create_t4 <- function(df, overall = FALSE) {
  df %>%
    select(dead28c,
           DischargeStatus,
           DischargeType,
           TotalCharge) %>%
    tbl_summary(
      by = dead28c,
      label = list(
        DischargeStatus ~ 'Discharge status (IDP only)',
        DischargeType   ~ 'Discharge type (IDP only)'
      ),
      missing = "no"
    ) %>%
    bold_labels() %>%
    # Add labels describing stat for each variable
    add_stat_label() %>%
    format_table_1(overall)
}
```

```{r data}
# Screening
df_scr <-
  read_sas(

   
    "C:/MyD/Sepsis_Pro/MF/tblPart1.sas7bdat",
    "C:/MyD/Sepsis_Pro/LABEL/prosepsis.sas7bcat"

  )

# Enrollment

df_enr <-
  read_sas(
    "C:/MyD/Sepsis_Pro/MF/psmast.sas7bdat",
    "C:/MyD/Sepsis_Pro/LABEL/prosepsis.sas7bcat"
    # "C:/Projects/ProSepsis/SAS/MF/psmast.sas7bdat",
    # "C:/Projects/ProSepsis/SAS/MF/prosepsis.sas7bcat"

  ) %>%
  mutate(
    dead28c = factor(
      dead28c,
      levels = c(1, 2),
      labels = c('Dead', 'Alive')
    ),
    sepsis = factor(
      Sofa_Sepsis,
      levels = c(1, 2),
      labels = c('Sepsis', 'Non-sepsis')
    ),
    across(
      c(
        Sex,
        PlaceChk_n,
        Occupation,
        OPD_IPD,
        Sepsis_Scale,
        HIV,
        Covid21,
        DischargeStatus,
        DischargeType,
        OPDOutcome,
        Outcome28Days,
        BMIgp
      ),
      ~ as_factor(.)
    ),
    across(
      c(
        Refer,
        SIRS,
        QSofa,
        UnSmoke:UnAlcohol,
        NP,
        CB,
        Sofa_Sepsis,
        HBsAgr,
        HBc,
        AntiHBs,
        AntiHCV,
        Influenza,
        Leptor,
        MalariaR,
        Melio,
        RSV,
        vasopressor,
        oxygensupp,
        Hypoglycemia
      ),
      ~ ifelse(. == 2, 0, .)
    ),
    covid19_r = ifelse(grepl('1', Covid_tests, fixed = TRUE), 1, 0),
    dengue_r  = ifelse(grepl('1', Dengue_tests, fixed = TRUE), 1, 0),
    denguel_r = ifelse(grepl('1', DengueL_tests, fixed = TRUE), 1, 0),
    hbshcv_r  = ifelse(grepl('1', HBSHCV_tests, fixed = TRUE), 1, 0),
    scrubt_r  = ifelse(grepl('1', ScrubT_tests, fixed = TRUE), 1, 0)
  )

var_label(df_enr) <- list(
  achromobacter    = paste0(var_label(df_enr$achromobacter), 
                            ' (', sum(df_enr$achromobacter_i),    ifelse(sum(df_enr$achromobacter_i) == 1,' isolation)',' isolations)')),
  acinetobacter_b = paste0(var_label(df_enr$acinetobacter_b),
                            ' (', sum(df_enr$acinetobacter_b_i),    ifelse(sum(df_enr$acinetobacter_b_i) == 1,' isolation)',' isolations)')),
  acinetobacter_l = paste0(var_label(df_enr$acinetobacter_l), 
                            ' (', sum(df_enr$acinetobacter_l_i),    ifelse(sum(df_enr$acinetobacter_l_i) == 1,' isolation)',' isolations)')),
  aerobic          = paste0(var_label(df_enr$aerobic), 
                            ' (', sum(df_enr$aerobic_i),          ifelse(sum(df_enr$aerobic_i) == 1,' isolation)',' isolations)')),
  aeromonas        = paste0(var_label(df_enr$aeromonas), 
                            ' (', sum(df_enr$aeromonas_i),        ifelse(sum(df_enr$aeromonas_i) == 1,' isolation)',' isolations)')),
  burkholderia_c   = paste0(var_label(df_enr$burkholderia_c), 
                            ' (', sum(df_enr$burkholderia_c_i),   ifelse(sum(df_enr$burkholderia_c_i) == 1,' isolation)',' isolations)')),
  burkholderia_p   = paste0(var_label(df_enr$burkholderia_p), 
                            ' (', sum(df_enr$burkholderia_p_i),   ifelse(sum(df_enr$burkholderia_p_i) == 1,' isolation)',' isolations)')),
  dermacoccus      = paste0(var_label(df_enr$dermacoccus), 
                            ' (', sum(df_enr$dermacoccus_i),      ifelse(sum(df_enr$dermacoccus_i) == 1,' isolation)',' isolations)')),
  edwardsiella     = paste0(var_label(df_enr$edwardsiella), 
                            ' (', sum(df_enr$edwardsiella_i),     ifelse(sum(df_enr$edwardsiella_i) == 1,' isolation)',' isolations)')),
  enterobacter     = paste0(var_label(df_enr$enterobacter), 
                            ' (', sum(df_enr$enterobacter_i),     ifelse(sum(df_enr$enterobacter_i) == 1,' isolation)',' isolations)')),
  enterococcus     = paste0(var_label(df_enr$enterococcus), 
                            ' (', sum(df_enr$enterococcus_i),     ifelse(sum(df_enr$enterococcus_i) == 1,' isolation)',' isolations)')),
  escherichia      = paste0(var_label(df_enr$escherichia), 
                            ' (', sum(df_enr$escherichia_i),      ifelse(sum(df_enr$escherichia_i) == 1,' isolation)',' isolations)')),
  haemophilus      = paste0(var_label(df_enr$haemophilus), 
                            ' (', sum(df_enr$haemophilus_i),      ifelse(sum(df_enr$haemophilus_i) == 1,' isolation)',' isolations)')),
  klebsiella       = paste0(var_label(df_enr$klebsiella), 
                            ' (', sum(df_enr$klebsiella_i),       ifelse(sum(df_enr$klebsiella_i) == 1,' isolation)',' isolations)')),
  kluyvera         = paste0(var_label(df_enr$kluyvera), 
                            ' (', sum(df_enr$kluyvera_i),         ifelse(sum(df_enr$kluyvera_i) == 1,' isolation)',' isolations)')),
  micrococcus      = paste0(var_label(df_enr$micrococcus), 
                            ' (', sum(df_enr$micrococcus_i),      ifelse(sum(df_enr$micrococcus_i) == 1,' isolation)',' isolations)')),
  morexella        = paste0(var_label(df_enr$morexella), 
                            ' (', sum(df_enr$morexella_i),        ifelse(sum(df_enr$morexella_i) == 1,' isolation)',' isolations)')),
  proteus          = paste0(var_label(df_enr$proteus), 
                            ' (', sum(df_enr$proteus_i),          ifelse(sum(df_enr$proteus_i) == 1,' isolation)',' isolations)')),
  providencia      = paste0(var_label(df_enr$providencia), 
                            ' (', sum(df_enr$providencia_i),      ifelse(sum(df_enr$providencia_i) == 1,' isolation)',' isolations)')),
  pseudohyphae     = paste0(var_label(df_enr$pseudohyphae), 
                            ' (', sum(df_enr$pseudohyphae_i),     ifelse(sum(df_enr$pseudohyphae_i) == 1,' isolation)',' isolations)')),
  salmonella       = paste0(var_label(df_enr$salmonella), 
                            ' (', sum(df_enr$salmonella_i),       ifelse(sum(df_enr$salmonella_i) == 1,' isolation)',' isolations)')),
  staphylococcus   = paste0(var_label(df_enr$staphylococcus), 
                            ' (', sum(df_enr$staphylococcus_i),   ifelse(sum(df_enr$staphylococcus_i) == 1,' isolation)',' isolations)')),
  stenotrophomonas = paste0(var_label(df_enr$stenotrophomonas), 
                            ' (', sum(df_enr$stenotrophomonas_i), ifelse(sum(df_enr$stenotrophomonas_i) == 1,' isolation)',' isolations)')),
  streptococcus_vi = paste0(var_label(df_enr$streptococcus_vi), 
                            ' (', sum(df_enr$streptococcus_vi_i), ifelse(sum(df_enr$streptococcus_vi_i) == 1,' isolation)',' isolations)')),
  streptococcus_an = paste0(var_label(df_enr$streptococcus_an), 
                            ' (', sum(df_enr$streptococcus_an_i), ifelse(sum(df_enr$streptococcus_an_i) == 1,' isolation)',' isolations)')),
  streptococcus_bo = paste0(var_label(df_enr$streptococcus_bo), 
                            ' (', sum(df_enr$streptococcus_bo_i), ifelse(sum(df_enr$streptococcus_bo_i) == 1,' isolation)',' isolations)')),
  streptococcus_co = paste0(var_label(df_enr$streptococcus_co), 
                            ' (', sum(df_enr$streptococcus_co_i), ifelse(sum(df_enr$streptococcus_co_i) == 1,' isolation)',' isolations)')),
  streptococcus_a  = paste0(var_label(df_enr$streptococcus_a), 
                            ' (', sum(df_enr$streptococcus_a_i),  ifelse(sum(df_enr$streptococcus_a_i) == 1,' isolation)',' isolations)')),
  streptococcus_b  = paste0(var_label(df_enr$streptococcus_b), 
                            ' (', sum(df_enr$streptococcus_b_i),  ifelse(sum(df_enr$streptococcus_b_i) == 1,' isolation)',' isolations)')),
  streptococcus_pn = paste0(var_label(df_enr$streptococcus_pn), 
                            ' (', sum(df_enr$streptococcus_pn_i), ifelse(sum(df_enr$streptococcus_pn_i) == 1,' isolation)',' isolations)')),
  streptococcus_su = paste0(var_label(df_enr$streptococcus_su), 
                            ' (', sum(df_enr$streptococcus_su_i), ifelse(sum(df_enr$streptococcus_sv_i) == 1,' isolation)',' isolations)')),
  vibrio           = paste0(var_label(df_enr$vibrio), 
                            ' (', sum(df_enr$vibrio_i),           ifelse(sum(df_enr$vibrio_i) == 1,' isolation)',' isolations)')),
  gramneg          = paste0(var_label(df_enr$gramneg), 
                            ' (', sum(df_enr$gramneg_i),          ifelse(sum(df_enr$gramneg_i) == 1,' isolation)',' isolations)')),
  grampos          = paste0(var_label(df_enr$grampos), 
                            ' (', sum(df_enr$grampos_i),          ifelse(sum(df_enr$grampos_i) == 1,' isolation)',' isolations)'))
)

df_enr_i <- filter(df_enr, OPD_IPD == '1 -IPD')
df_enr_o <- filter(df_enr, OPD_IPD == '2 -OPD')

n_enr  <- nrow(df_enr)
n_miss <- sum(is.na(df_enr$dead28c), na.rm = TRUE)
# n_miss_i <- sum(is.na(df_enr_i$dead28c), na.rm = TRUE)
# n_miss_o <- sum(is.na(df_enr_o$dead28c), na.rm = TRUE)
n_amr <- sum(df_enr$total_org > 0, na.rm = TRUE)
```

<br><br> **Figure 1**: Flow chart presenting the number of screening and enroll patients with sepsis who participating in this sepsis epidemiology activities

<center>

```{r flowchart}
 source("flowchart.R", local = knitr::knit_global())
 d
```

</center>

<br>

\newpage

**Table 1**: Descriptive statistical analysis of the baseline demographic data and clinical characteristics of the enrolled suspected sepsis cases at Nakhon Phanom and Mae Sot hospitals during November 2021- July 8, 2022 (N=`r n_enr`)

```{r t1}
t1t <- create_t1(df_enr, TRUE)
t1i <- create_t1(df_enr_i)
t1o <- create_t1(df_enr_o)
t1  <- tbl_merge(list(t1t, t1i, t1o),
                 tab_spanner = c("**Total**", "**IPD**", "**OPD**"))

t1t_cc <- create_t1_cc(df_enr, TRUE)
t1i_cc <- create_t1_cc(df_enr_i)
t1o_cc <- create_t1_cc(df_enr_o)
t1_cc  <- tbl_merge(list(t1t_cc, t1i_cc, t1o_cc),
                    tab_spanner = c("**Total**", "**IPD**", "**OPD**"))

t1t_if <- create_t1_if(df_enr, TRUE)
t1i_if <- create_t1_if(df_enr_i)
t1o_if <- create_t1_if(df_enr_o)
t1_if  <- tbl_merge(list(t1t_if, t1i_if, t1o_if),
                    tab_spanner = c("**Total**", "**IPD**", "**OPD**"))

t1 <- tbl_stack(list(t1, t1_cc, t1_if),
                group_header = c('', 'Chief Complaint, n (%)', 'Source of Infection, n (%)')) %>%
  format_table_2() %>%
  tab_style(style = cell_borders(sides = "bottom", style = "hidden"),
            locations = cells_row_groups(groups = 1))

t1
```

<br>

\newpage

**Table 2**: Clinical information and laboratory result of enrolled suspected sepsis cases participating at Nakhon Phanom and Mae Sot hospitals during November 2021- July 8, 2022 (N=`r n_enr`)

```{r t2}
t2t <- create_t2(df_enr, TRUE)
t2i <- create_t2(df_enr_i)
t2o <- create_t2(df_enr_o)
t2  <- tbl_merge(list(t2t, t2i, t2o),
                    tab_spanner = c("**Total**", "**IPD**", "**OPD**"))

t2t_un <- create_t2_un(df_enr, TRUE)
t2i_un <- create_t2_un(df_enr_i)
t2o_un <- create_t2_un(df_enr_o)
t2_un  <- tbl_merge(list(t2t_un, t2i_un, t2o_un),
                    tab_spanner = c("**Total**", "**IPD**", "**OPD**"))

t2t_risk <- create_t2_risk(df_enr, TRUE)
t2i_risk <- create_t2_risk(df_enr_i)
t2o_risk <- create_t2_risk(df_enr_o)
t2_risk  <- tbl_merge(list(t2t_risk, t2i_risk, t2o_risk),
                      tab_spanner = c("**Total**", "**IPD**", "**OPD**"))

t2t_pui <- create_t2_pui(df_enr, TRUE)
t2i_pui <- create_t2_pui(df_enr_i)
t2o_pui <- create_t2_pui(df_enr_o)
t2_pui  <- tbl_merge(list(t2t_pui, t2i_pui, t2o_pui),
                     tab_spanner = c("**Total**", "**IPD**", "**OPD**"))

t2t_dx <- create_t2_dx(df_enr, TRUE)
t2i_dx <- create_t2_dx(df_enr_i)
t2o_dx <- create_t2_dx(df_enr_o)
t2_dx  <- tbl_merge(list(t2t_dx, t2i_dx, t2o_dx),
                    tab_spanner = c("**Total**", "**IPD**", "**OPD**"))

t2t_or <- create_t2_or(df_enr, TRUE)
t2i_or <- create_t2_or(df_enr_i)
t2o_or <- create_t2_or(df_enr_o)
t2_or  <- tbl_merge(list(t2t_or, t2i_or, t2o_or),
                    tab_spanner = c("**Total**", "**IPD**", "**OPD**"))

t2t_cul_s <- create_t2_cul_s(df_enr, TRUE)
t2i_cul_s <- create_t2_cul_s(df_enr_i)
t2o_cul_s <- create_t2_cul_s(df_enr_o)
t2_cul_s  <- tbl_merge(list(t2t_cul_s, t2i_cul_s, t2o_cul_s),
                       tab_spanner = c("**Total**", "**IPD**", "**OPD**"))

t2t_rdt <- create_t2_rdt(df_enr, TRUE)
t2i_rdt <- create_t2_rdt(df_enr_i)
t2o_rdt <- create_t2_rdt(df_enr_o)
t2_rdt  <- tbl_merge(list(t2t_rdt, t2i_rdt, t2o_rdt),
                     tab_spanner = c("**Total**", "**IPD**", "**OPD**"))

t2t_trt <- create_t2_trt(df_enr, TRUE)
t2i_trt <- create_t2_trt(df_enr_i)
t2o_trt <- create_t2_trt(df_enr_o)
t2_trt  <- tbl_merge(list(t2t_trt, t2i_trt, t2o_trt),
                     tab_spanner = c("**Total**", "**IPD**", "**OPD**"))

t2 <- tbl_stack(list(t2, t2_un, t2_risk, t2_pui, t2_dx, t2_or, t2_cul_s, t2_rdt, t2_trt),
                group_header = c('',
                                 'Underlying Condition/Co-morbidity, n (%)',
                                 'Risk Behavior, n (%)',
                                 'PUI (SARS-CoV2 NGS and TAC), n (%)',
                                 'Provisional Diagnosis, n (%)',
                                 'Organ Dysfunction, n (%)',
                                 'Microbiology: Culture Source, n (%)',
                                 'RDT, n (%)',
                                 'Treatment (received), n (%)')) %>%
  format_table_2()
t2
```

<br>

\newpage

**Table 3**: Microbiological blood culture results and multidrug resistance profile of common bacterial pathogens causing of sepsis (N=`r n_amr`)
<br>
Dead vs Alive
```{r t3a}
t3at <- create_t3(df_enr, overall = TRUE)
t3ai <- create_t3(df_enr_i)
t3ao <- create_t3(df_enr_o)
t3a  <- tbl_merge(list(t3at, t3ai, t3ao),
                  tab_spanner = c("**Total**", "**IPD**", "**OPD**"))
t3a  <- format_table_2(t3a)
t3a
```

<br>
Sepsis vs Non-sepsis
```{r t3b}
t3bt <- create_t3(df_enr, sepsis, TRUE)
t3bi <- create_t3(df_enr_i, sepsis)
t3bo <- create_t3(df_enr_o, sepsis)
t3b  <- tbl_merge(list(t3bt, t3bi, t3bo),
                  tab_spanner = c("**Total**", "**IPD**", "**OPD**"))
t3b  <- format_table_2(t3b)
t3b
```

<br>

\newpage

**Table 4**: Bivariate analysis discharge outcome of patient with sepsis activities at Nakhon Phanom and Mae Sot hospitals during November 2021- July 8, 2022 (N=`r n_enr`)

```{r t4}
t4t_dx <- create_t4_dx(df_enr, TRUE)
t4i_dx <- create_t4_dx(df_enr_i)
t4o_dx <- create_t4_dx(df_enr_o)
t4_dx  <- tbl_merge(list(t4t_dx, t4i_dx, t4o_dx),
                    tab_spanner = c("**Total**", "**IPD**", "**OPD**"))

t4t <- create_t4(df_enr, TRUE)
t4i <- create_t4(df_enr_i)
t4o <- create_t4(df_enr_o)
t4  <- tbl_merge(list(t4t, t4i, t4o),
                 tab_spanner = c("**Total**", "**IPD**", "**OPD**"))

t4 <- tbl_stack(list(t4_dx, t4),
                group_header = c('Principal diagnosis, n (%)', '')) %>%
  format_table_2() %>%
  tab_style(style = cell_borders(sides = "bottom", style = 'hidden'),
            locations = cells_row_groups(groups = 2))
t4
```

```{r}
# uni <- df_enr %>%
#   select(Age_year, Sex, Refer, Sepsis:Cancer, Liver, TotalCharge, dead28c, stime) %>%
#   mutate(dead28c = ifelse(dead28c == 0, 2, dead28c)) %>%
#   tbl_uvregression(method = coxph,
#                    y = Surv(stime, dead28c),
#                    exponentiate = TRUE) %>%
#   add_global_p()
# uni
```
