---
title: "Pro-sepsis"
#author: "Nartlada Chantharojwong & Vorapathu Thaineua"
date: "Compiled on `r format(Sys.time(), '%B %d, %Y - %H:%M')`"
output:
  html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  cache = FALSE
)

library(tidyverse)
library(haven)      # Read SAS dataset
library(purrr)      # Apply function (sum) to each element
library(scales)     # Format numeric values
library(labelled)   # Set organism variable labels
library(DiagrammeR) # Create flowchart
library(gtsummary)  # Create publication-ready summary tables
library(survival)   # Survival analysis
library(gt)         # Format gtsummary output

theme_gtsummary_compact(font_size = 10)
```

```{r functions}
# Format gtsummary outputs after merging
format_table <- function(t) {

  gt <- t %>%
    # Convert to gt and use default left align
    as_gt() %>%
    # Standard column width to fit every table
    cols_width(
      label ~ px(230),
      stat_0_1 ~ px(100),
      starts_with('p.value') ~ px(50),
      everything() ~ px(70)
    ) %>%
    tab_style(
      style = cell_text(weight = "bold"),
      locations = cells_row_groups()) %>%
    tab_style(
      style = cell_text(weight = "bold"),
      locations = cells_body(
        columns = label,
        rows = variable %in% c(
          "gramneg",
          "grampos",
          "gramneg_m",
          "grampos_m"
        )
      )
    ) %>%
    tab_options(
      # row_group.border.top.width = 1,
      # row_group.border.bottom.width = 1,
      table.border.bottom.style = "hidden"
    )

  return(gt)

}

# Sort dichotomous variables by descending frequency
sort_var <- function(df, ...) {
    df %>%
    filter(!is.na(dead28c)) %>%
    select(...) %>%
    map_dbl(sum, na.rm = TRUE) %>%
    sort(decreasing = TRUE)
}

create_tt <- function(df,
                      vars,
                      bold = TRUE,
                      label = '') {
  t <- tbl_summary(df %>% select(vars), 
                   by = dead28c,
                   missing = "no") %>%
    add_p(test.args = all_tests("fisher.test") ~ list(workspace = 2e9)) %>%
    # Bold p-value if significant
    bold_p(t = 0.05) %>%
    modify_header(update = list(label ~ label,
                                stat_0 ~ "**Overall**<br>N = {N}")) %>% 
    modify_footnote(update = stat_0 ~ NA)
  if (bold == TRUE) {
    t <- t %>% bold_labels() %>%
      add_stat_label()
  }
  return(t)
}

create_ts <- function(df, vars) {
  tbl_strata(
    df %>% select(sepsis, dead28c, vars),
    strata = sepsis,
    .tbl_fun =
      ~ .x %>%
      tbl_summary(by = dead28c,
                  missing = "no") %>%
      add_p(test.args = all_tests("fisher.test") ~ list(workspace = 2e9)) %>%
      # Bold p-value if significant
      bold_p(t = 0.05) %>%
      bold_labels() %>%
      add_stat_label() %>%
      modify_header(update = list(
        label ~ "",
        all_stat_cols() ~ "**{level}**<br>N = {n}"
      )) %>%
      modify_footnote(update = all_stat_cols() ~ NA),
    .header = "**{strata}**, N = {n}"
  )
}

create_ts2 <- function(df, vars) {
  tbl_strata(
    df %>% select(sepsis, dead28c, vars),
    strata = sepsis,
    .tbl_fun =
      ~ .x %>%
      tbl_summary(by = dead28c,
                  missing = "no") %>%
      add_p(test.args = all_tests("fisher.test") ~ list(workspace = 2e9)) %>%
      # Bold p-value if significant
      bold_p(t = 0.05) %>%
      modify_header(update = list(
        label ~ "",
        all_stat_cols() ~ "**{level}**<br>N = {n}"
      )) %>%
      modify_footnote(update = all_stat_cols() ~ NA),
    .header = "**{strata}**, N = {n}"
  )
}

create_t3 <- function(df, outcome = dead28c, vars) {
  outcome = enquo(outcome)
  df %>%
    select(!!outcome, vars) %>%
    tbl_summary(by = !!outcome) %>% 
    add_p(test.args = all_tests("fisher.test") ~ list(workspace = 2e9)) %>%
    # Bold p-value if significant
    bold_p(t = 0.05) %>%
    modify_footnote(update = all_stat_cols() ~ NA)
}
```

```{r data}
# Screening
df_scr <-
  read_sas(
    "C:/MyD/Sepsis_Pro/MF/tblPart1.sas7bdat",
    "C:/MyD/Sepsis_Pro/LABEL/prosepsis.sas7bcat"
    # "C:/Projects/ProSepsis/SAS/MF/tblPart1.sas7bdat",
    # "C:/Projects/ProSepsis/SAS/LABEL/prosepsis.sas7bcat"
  )

# Enrollment
df_enr <-
  read_sas(
    "C:/MyD/Sepsis_Pro/MF/psmast.sas7bdat",
    "C:/MyD/Sepsis_Pro/LABEL/prosepsis.sas7bcat"
    # "C:/Projects/ProSepsis/SAS/MF/psmast.sas7bdat",
    # "C:/Projects/ProSepsis/SAS/LABEL/prosepsis.sas7bcat"
  ) %>%
  mutate(
    dead28c = factor(
      dead28c,
      levels = c(1, 2),
      labels = c('Dead', 'Alive')
    ),
    sepsis = factor(
      Review_Sepsisr,
      levels = c(2,1),
      labels = c( 'Non-sepsis','Sepsis')
    ),
    across(
      c(
        Sex,
        BMIgp,
        PlaceChk_n,
        Occupation,
        OPD_IPD,
        Sepsis_Scale,
        HIV,
        Covid21,
        DischargeStatus,
        DischargeType
      ),
      ~ as_factor(.)
    ),
    across(
      c(
        Refer,
        QSofa,
        UnSmoke:UnAlcohol,
        NP,
        CB,
        Sofa_Sepsis,
        vasopressor,
        oxygensupp,
        Hypoglycemia,
        HBsAgr,
        HBc,
        AntiHBs,
        AntiHCV,
        Influenza,
        Leptor,
        MalariaR,
        Melio,
        RSV
      ),
      ~ ifelse(. == 2, 0, .)
    ),
    covid19_r = ifelse(grepl('1', Covid_tests, fixed = TRUE), 1, 0),
    dengue_r  = ifelse(grepl('1', Dengue_tests, fixed = TRUE), 1, 0),
    denguel_r = ifelse(grepl('1', DengueL_tests, fixed = TRUE), 1, 0),
    hbshcv_r  = ifelse(grepl('1', HBSHCV_tests, fixed = TRUE), 1, 0),
    scrubt_r  = ifelse(grepl('1', ScrubT_tests, fixed = TRUE), 1, 0)
  )

var_label(df_enr) <- list(
  achromobacter      = paste0(var_label(df_enr$achromobacter),
                              ' (', sum(df_enr$achromobacter_i),    ifelse(sum(df_enr$achromobacter_i) == 1,' isolation)',' isolations)')),
  acinetobacter_b    = paste0(var_label(df_enr$acinetobacter_b),
                              ' (', sum(df_enr$acinetobacter_b_i),  ifelse(sum(df_enr$acinetobacter_b_i) == 1,' isolation)',' isolations)')),
  acinetobacter_l    = paste0(var_label(df_enr$acinetobacter_l),
                              ' (', sum(df_enr$acinetobacter_l_i),  ifelse(sum(df_enr$acinetobacter_l_i) == 1,' isolation)',' isolations)')),
  aerobic            = paste0(var_label(df_enr$aerobic),
                              ' (', sum(df_enr$aerobic_i),          ifelse(sum(df_enr$aerobic_i) == 1,' isolation)',' isolations)')),
  aeromonas          = paste0(var_label(df_enr$aeromonas),
                              ' (', sum(df_enr$aeromonas_i),        ifelse(sum(df_enr$aeromonas_i) == 1,' isolation)',' isolations)')),
  burkholderia_c     = paste0(var_label(df_enr$burkholderia_c),
                              ' (', sum(df_enr$burkholderia_c_i),   ifelse(sum(df_enr$burkholderia_c_i) == 1,' isolation)',' isolations)')),
  burkholderia_p     = paste0(var_label(df_enr$burkholderia_p),
                              ' (', sum(df_enr$burkholderia_p_i),   ifelse(sum(df_enr$burkholderia_p_i) == 1,' isolation)',' isolations)')),
  dermacoccus        = paste0(var_label(df_enr$dermacoccus),
                              ' (', sum(df_enr$dermacoccus_i),      ifelse(sum(df_enr$dermacoccus_i) == 1,' isolation)',' isolations)')),
  edwardsiella       = paste0(var_label(df_enr$edwardsiella),
                              ' (', sum(df_enr$edwardsiella_i),     ifelse(sum(df_enr$edwardsiella_i) == 1,' isolation)',' isolations)')),
  enterobacter       = paste0(var_label(df_enr$enterobacter),
                              ' (', sum(df_enr$enterobacter_i),     ifelse(sum(df_enr$enterobacter_i) == 1,' isolation)',' isolations)')),
  enterococcus       = paste0(var_label(df_enr$enterococcus),
                              ' (', sum(df_enr$enterococcus_i),     ifelse(sum(df_enr$enterococcus_i) == 1,' isolation)',' isolations)')),
  escherichia        = paste0(var_label(df_enr$escherichia),
                              ' (', sum(df_enr$escherichia_i),      ifelse(sum(df_enr$escherichia_i) == 1,' isolation)',' isolations)')),
  haemophilus        = paste0(var_label(df_enr$haemophilus),
                              ' (', sum(df_enr$haemophilus_i),      ifelse(sum(df_enr$haemophilus_i) == 1,' isolation)',' isolations)')),
  klebsiella         = paste0(var_label(df_enr$klebsiella),
                              ' (', sum(df_enr$klebsiella_i),       ifelse(sum(df_enr$klebsiella_i) == 1,' isolation)',' isolations)')),
  kluyvera           = paste0(var_label(df_enr$kluyvera),
                              ' (', sum(df_enr$kluyvera_i),         ifelse(sum(df_enr$kluyvera_i) == 1,' isolation)',' isolations)')),
  micrococcus        = paste0(var_label(df_enr$micrococcus),
                              ' (', sum(df_enr$micrococcus_i),      ifelse(sum(df_enr$micrococcus_i) == 1,' isolation)',' isolations)')),
  morexella          = paste0(var_label(df_enr$morexella),
                              ' (', sum(df_enr$morexella_i),        ifelse(sum(df_enr$morexella_i) == 1,' isolation)',' isolations)')),
  proteus            = paste0(var_label(df_enr$proteus),
                              ' (', sum(df_enr$proteus_i),          ifelse(sum(df_enr$proteus_i) == 1,' isolation)',' isolations)')),
  providencia        = paste0(var_label(df_enr$providencia),
                              ' (', sum(df_enr$providencia_i),      ifelse(sum(df_enr$providencia_i) == 1,' isolation)',' isolations)')),
  pseudohyphae       = paste0(var_label(df_enr$pseudohyphae),
                              ' (', sum(df_enr$pseudohyphae_i),     ifelse(sum(df_enr$pseudohyphae_i) == 1,' isolation)',' isolations)')),
  salmonella         = paste0(var_label(df_enr$salmonella),
                              ' (', sum(df_enr$salmonella_i),       ifelse(sum(df_enr$salmonella_i) == 1,' isolation)',' isolations)')),
  staphylococcus     = paste0(var_label(df_enr$staphylococcus),
                              ' (', sum(df_enr$staphylococcus_i),   ifelse(sum(df_enr$staphylococcus_i) == 1,' isolation)',' isolations)')),
  stenotrophomonas   = paste0(var_label(df_enr$stenotrophomonas),
                              ' (', sum(df_enr$stenotrophomonas_i), ifelse(sum(df_enr$stenotrophomonas_i) == 1,' isolation)',' isolations)')),
  streptococcus_vi   = paste0(var_label(df_enr$streptococcus_vi),
                              ' (', sum(df_enr$streptococcus_vi_i), ifelse(sum(df_enr$streptococcus_vi_i) == 1,' isolation)',' isolations)')),
  streptococcus_an   = paste0(var_label(df_enr$streptococcus_an),
                              ' (', sum(df_enr$streptococcus_an_i), ifelse(sum(df_enr$streptococcus_an_i) == 1,' isolation)',' isolations)')),
  streptococcus_bo   = paste0(var_label(df_enr$streptococcus_bo),
                              ' (', sum(df_enr$streptococcus_bo_i), ifelse(sum(df_enr$streptococcus_bo_i) == 1,' isolation)',' isolations)')),
  streptococcus_co   = paste0(var_label(df_enr$streptococcus_co),
                              ' (', sum(df_enr$streptococcus_co_i), ifelse(sum(df_enr$streptococcus_co_i) == 1,' isolation)',' isolations)')),
  streptococcus_a    = paste0(var_label(df_enr$streptococcus_a),
                              ' (', sum(df_enr$streptococcus_a_i),  ifelse(sum(df_enr$streptococcus_a_i) == 1,' isolation)',' isolations)')),
  streptococcus_b    = paste0(var_label(df_enr$streptococcus_b),
                              ' (', sum(df_enr$streptococcus_b_i),  ifelse(sum(df_enr$streptococcus_b_i) == 1,' isolation)',' isolations)')),
  streptococcus_pn   = paste0(var_label(df_enr$streptococcus_pn),
                              ' (', sum(df_enr$streptococcus_pn_i), ifelse(sum(df_enr$streptococcus_pn_i) == 1,' isolation)',' isolations)')),
  streptococcus_su   = paste0(var_label(df_enr$streptococcus_su),
                              ' (', sum(df_enr$streptococcus_su_i), ifelse(sum(df_enr$streptococcus_su_i) == 1,' isolation)',' isolations)')),
  vibrio             = paste0(var_label(df_enr$vibrio),
                              ' (', sum(df_enr$vibrio_i),           ifelse(sum(df_enr$vibrio_i) == 1,' isolation)',' isolations)')),
  gramneg            = paste0(var_label(df_enr$gramneg),
                              ' (', sum(df_enr$gramneg_i),          ifelse(sum(df_enr$gramneg_i) == 1,' isolation)',' isolations)')),
  grampos            = paste0(var_label(df_enr$grampos),
                              ' (', sum(df_enr$grampos_i),          ifelse(sum(df_enr$grampos_i) == 1,' isolation)',' isolations)')),
  achromobacter_m    = paste0(var_label(df_enr$achromobacter),
                              ' (', sum(df_enr$achromobacter_i),    ifelse(sum(df_enr$achromobacter_i) == 1,' isolation)',' isolations)')),
  acinetobacter_b_m  = paste0(var_label(df_enr$acinetobacter_b),
                              ' (', sum(df_enr$acinetobacter_b_i),  ifelse(sum(df_enr$acinetobacter_b_i) == 1,' isolation)',' isolations)')),
  acinetobacter_l_m  = paste0(var_label(df_enr$acinetobacter_l),
                              ' (', sum(df_enr$acinetobacter_l_i),  ifelse(sum(df_enr$acinetobacter_l_i) == 1,' isolation)',' isolations)')),
  aerobic_m          = paste0(var_label(df_enr$aerobic),
                              ' (', sum(df_enr$aerobic_i),          ifelse(sum(df_enr$aerobic_i) == 1,' isolation)',' isolations)')),
  aeromonas_m        = paste0(var_label(df_enr$aeromonas),
                              ' (', sum(df_enr$aeromonas_i),        ifelse(sum(df_enr$aeromonas_i) == 1,' isolation)',' isolations)')),
  burkholderia_c_m   = paste0(var_label(df_enr$burkholderia_c),
                              ' (', sum(df_enr$burkholderia_c_i),   ifelse(sum(df_enr$burkholderia_c_i) == 1,' isolation)',' isolations)')),
  burkholderia_p_m   = paste0(var_label(df_enr$burkholderia_p),
                              ' (', sum(df_enr$burkholderia_p_i),   ifelse(sum(df_enr$burkholderia_p_i) == 1,' isolation)',' isolations)')),
  dermacoccus_m      = paste0(var_label(df_enr$dermacoccus),
                              ' (', sum(df_enr$dermacoccus_i),      ifelse(sum(df_enr$dermacoccus_i) == 1,' isolation)',' isolations)')),
  edwardsiella_m     = paste0(var_label(df_enr$edwardsiella),
                              ' (', sum(df_enr$edwardsiella_i),     ifelse(sum(df_enr$edwardsiella_i) == 1,' isolation)',' isolations)')),
  enterobacter_m     = paste0(var_label(df_enr$enterobacter),
                              ' (', sum(df_enr$enterobacter_i),     ifelse(sum(df_enr$enterobacter_i) == 1,' isolation)',' isolations)')),
  enterococcus_m     = paste0(var_label(df_enr$enterococcus),
                              ' (', sum(df_enr$enterococcus_i),     ifelse(sum(df_enr$enterococcus_i) == 1,' isolation)',' isolations)')),
  escherichia_m      = paste0(var_label(df_enr$escherichia),
                              ' (', sum(df_enr$escherichia_i),      ifelse(sum(df_enr$escherichia_i) == 1,' isolation)',' isolations)')),
  haemophilus_m      = paste0(var_label(df_enr$haemophilus),
                              ' (', sum(df_enr$haemophilus_i),      ifelse(sum(df_enr$haemophilus_i) == 1,' isolation)',' isolations)')),
  klebsiella_m       = paste0(var_label(df_enr$klebsiella),
                              ' (', sum(df_enr$klebsiella_i),       ifelse(sum(df_enr$klebsiella_i) == 1,' isolation)',' isolations)')),
  kluyvera_m         = paste0(var_label(df_enr$kluyvera),
                              ' (', sum(df_enr$kluyvera_i),         ifelse(sum(df_enr$kluyvera_i) == 1,' isolation)',' isolations)')),
  micrococcus_m      = paste0(var_label(df_enr$micrococcus),
                              ' (', sum(df_enr$micrococcus_i),      ifelse(sum(df_enr$micrococcus_i) == 1,' isolation)',' isolations)')),
  morexella_m        = paste0(var_label(df_enr$morexella),
                              ' (', sum(df_enr$morexella_i),        ifelse(sum(df_enr$morexella_i) == 1,' isolation)',' isolations)')),
  proteus_m          = paste0(var_label(df_enr$proteus),
                              ' (', sum(df_enr$proteus_i),          ifelse(sum(df_enr$proteus_i) == 1,' isolation)',' isolations)')),
  providencia_m      = paste0(var_label(df_enr$providencia),
                              ' (', sum(df_enr$providencia_i),      ifelse(sum(df_enr$providencia_i) == 1,' isolation)',' isolations)')),
  pseudohyphae_m     = paste0(var_label(df_enr$pseudohyphae),
                              ' (', sum(df_enr$pseudohyphae_i),     ifelse(sum(df_enr$pseudohyphae_i) == 1,' isolation)',' isolations)')),
  salmonella_m       = paste0(var_label(df_enr$salmonella),
                              ' (', sum(df_enr$salmonella_i),       ifelse(sum(df_enr$salmonella_i) == 1,' isolation)',' isolations)')),
  staphylococcus_m   = paste0(var_label(df_enr$staphylococcus),
                              ' (', sum(df_enr$staphylococcus_i),   ifelse(sum(df_enr$staphylococcus_i) == 1,' isolation)',' isolations)')),
  stenotrophomonas_m = paste0(var_label(df_enr$stenotrophomonas),
                              ' (', sum(df_enr$stenotrophomonas_i), ifelse(sum(df_enr$stenotrophomonas_i) == 1,' isolation)',' isolations)')),
  streptococcus_vi_m = paste0(var_label(df_enr$streptococcus_vi),
                              ' (', sum(df_enr$streptococcus_vi_i), ifelse(sum(df_enr$streptococcus_vi_i) == 1,' isolation)',' isolations)')),
  streptococcus_an_m = paste0(var_label(df_enr$streptococcus_an),
                              ' (', sum(df_enr$streptococcus_an_i), ifelse(sum(df_enr$streptococcus_an_i) == 1,' isolation)',' isolations)')),
  streptococcus_bo_m = paste0(var_label(df_enr$streptococcus_bo),
                              ' (', sum(df_enr$streptococcus_bo_i), ifelse(sum(df_enr$streptococcus_bo_i) == 1,' isolation)',' isolations)')),
  streptococcus_co_m = paste0(var_label(df_enr$streptococcus_co),
                              ' (', sum(df_enr$streptococcus_co_i), ifelse(sum(df_enr$streptococcus_co_i) == 1,' isolation)',' isolations)')),
  streptococcus_a_m  = paste0(var_label(df_enr$streptococcus_a),
                              ' (', sum(df_enr$streptococcus_a_i),  ifelse(sum(df_enr$streptococcus_a_i) == 1,' isolation)',' isolations)')),
  streptococcus_b_m  = paste0(var_label(df_enr$streptococcus_b),
                              ' (', sum(df_enr$streptococcus_b_i),  ifelse(sum(df_enr$streptococcus_b_i) == 1,' isolation)',' isolations)')),
  streptococcus_pn_m = paste0(var_label(df_enr$streptococcus_pn),
                              ' (', sum(df_enr$streptococcus_pn_i), ifelse(sum(df_enr$streptococcus_pn_i) == 1,' isolation)',' isolations)')),
  streptococcus_su_m = paste0(var_label(df_enr$streptococcus_su),
                              ' (', sum(df_enr$streptococcus_su_i), ifelse(sum(df_enr$streptococcus_su_i) == 1,' isolation)',' isolations)')),
  vibrio_m           = paste0(var_label(df_enr$vibrio),
                              ' (', sum(df_enr$vibrio_i),           ifelse(sum(df_enr$vibrio_i) == 1,' isolation)',' isolations)')),
  gramneg_m          = paste0(var_label(df_enr$gramneg),
                              ' (', sum(df_enr$gramneg_i),          ifelse(sum(df_enr$gramneg_i) == 1,' isolation)',' isolations)')),
  grampos_m          = paste0(var_label(df_enr$grampos),
                              ' (', sum(df_enr$grampos_i),          ifelse(sum(df_enr$grampos_i) == 1,' isolation)',' isolations)'))
)

df_ipd <- filter(df_enr,OPD_IPD == "1 -IPD")
n_ipd  <- nrow(df_ipd)
```

<br><br> **Figure 1**: Flow chart presenting the number of screening and enroll patients with sepsis who participating in this sepsis epidemiology activities

<center>

```{r flowchart}
 source("flowchart.R", local = knitr::knit_global())
 d
```

</center>

<br>

\newpage

**Table 1**: Descriptive statistical analysis of the baseline demographic data and clinical characteristics of the enrolled suspected sepsis cases at Nakhon Phanom and Mae Sot hospitals during November 2021- July 8, 2022 (N=`r n_ipd`)

```{r t1}
df <- df_ipd %>%
  mutate(Age_gp4 = cut(
    Age_year,
    breaks = c(0, 14, 44, 64 , Inf),
    labels = c('<15', '15-44', '45-64', '>64')
  )) %>%
  select(
    sepsis,
    dead28c,
    Age_year,
    Age_gp4,
    Sex,
    BMIgp,
    PlaceChk_n,
    Occupation,
    Refer,
    QSofa,
    Sepsis_Scale,
    CCFever:CCJointPain,
    CCOther,
    IFTropSep:IFNerve,
    IFOth
  ) %>%
  set_variable_labels(
    Age_year     = 'Age',
    Age_gp4      = 'Age group',
    BMIgp        = 'BMI range',
    PlaceChk_n   = 'Admission ward',
    Refer        = 'Transferred',
    QSofa        = '(Any) qSOFA >= 2 scores',
    Sepsis_Scale = 'Sepsis determination (SOFA)',
    IFTropSep     = 'Tropical infection',
    IFRespiratory = 'Respiratory',
    IFBlood       = 'Blood',
    IFGas         = 'Gastrointestinal track',
    IFUrine       = 'Urinary',
    IFSkin        = 'Skin/Soft tissue/bone',
    IFNerve       = 'Central nervous system',
    IFOth         = 'Others'
  ) %>% 
  zap_labels()

vars <- names(select(df, Age_year:Sepsis_Scale))
t1t <- create_tt(df, vars)
t1s <- create_ts(df, vars)
t1  <- tbl_merge(list(t1t, t1s), tab_spanner = FALSE)

vars <- append(names(sort_var(df, CCFever:CCJointPain)), 'CCOther')
t1t_cc <- create_tt(df, vars, FALSE)
t1s_cc <- create_ts2(df, vars)
t1_cc  <- tbl_merge(list(t1t_cc, t1s_cc), tab_spanner = FALSE)

vars <- append(names(sort_var(df, IFTropSep:IFNerve)), 'IFOth')
t1t_if <- create_tt(df, vars, FALSE)
t1s_if <- create_ts2(df, vars)
t1_if  <- tbl_merge(list(t1t_if, t1s_if), tab_spanner = FALSE)

t1 <- tbl_stack(list(t1, t1_cc, t1_if),
                group_header = c('', 'Chief Complaint, n (%)', 'Source of Infection, n (%)')) %>%
  format_table() %>%
  tab_style(style = cell_borders(sides = "bottom", style = "hidden"),
            locations = cells_row_groups(groups = 1))
t1
```

<br>

\newpage

**Table 2**: Clinical information and laboratory result of enrolled suspected sepsis cases participating at Nakhon Phanom and Mae Sot hospitals during November 2021- July 8, 2022 (N=`r n_ipd`)

```{r t2}
df <- df_ipd %>%
  mutate(SOFA1 = ifelse(SOFA1 >= 3, 1, 0),
         across(SOFA2:SOFA6, ~ ifelse(. > 1, 1, .))) %>%
  select(sepsis, dead28c, 
         UnDiabetes:UnThalassemia, UnOth,
         UnSmoke:UnAlcohol, HIV, Covid21,
         NP, CB,
         DxFever:DxMening, DxOther,
         SOFA1:SOFA6, Sofa_Sepsis,
         OxyInbu, vasopressor, oxygensupp, Hypoglycemia,
         CulBlood_ever:CulOther_ever,
         covid19_r:denguel_r, HBsAgr, HBc, AntiHBs, AntiHCV, hbshcv_r, Influenza, Leptor, MalariaR, Melio, scrubt_r, RSV,
         penicillin_ever:parasitedrug_ever, otheranti_ever
  ) %>%
  set_variable_labels(
    UnRenal           = 'Renal disease',
    UnSmoke           = 'Smoking',
    UnAlcohol         = 'Alcohol',
    DxDengueFever     = 'Dengue fever',
    DxNecro           = 'Necrotizing fasciitis',
    SOFA1             = 'RS (PaO2/Fio2 < 200 with respiratory support',
    SOFA2             = 'Liver (Bilirubin > 1.2 mg/dl)',
    SOFA3             = 'Cardiovascular (MAP < 70 mmHg)',
    SOFA4             = 'CNS (Glasgow Coma Scale < 15)',
    SOFA5             = 'Blood (Platelet < 150,000 /μl)',
    SOFA6             = 'Renal (Cr > 1.2 mg/dl)',
    Sofa_Sepsis       = 'Sepsis: SOFA_Total >= 2',
    OxyInbu           = 'Ventilator use',
    vasopressor       = 'Vasopressor use',
    oxygensupp        = 'Supplement Oxygen',
    Hypoglycemia      = 'Hypoglycemia',
    CulBlood_ever     = 'Blood',
    CulSputum_ever    = 'Sputum',
    CulUrine_ever     = 'Urine',
    CulCSF_ever       = 'CSF',
    CulOther_ever     = 'Others',
    covid19_r         = 'COVID-19 +',
    dengue_r          = 'Dengue +',
    denguel_r         = 'Dengue + (lab)',
    HBsAgr            = 'HBsAg +',
    HBc               = 'HBc +',
    AntiHBs           = 'Anti-HBs +',
    AntiHCV           = 'Anti-HCV +',
    hbshcv_r          = 'Anti-HBs/Anti-HCV +',
    Influenza         = 'Influenza +',
    Leptor            = 'Leptospirosis +',
    MalariaR          = 'Malaria +',
    Melio             = 'Melioidosis +',
    scrubt_r          = 'Scrub typhus +',
    RSV               = 'RSV +',
    penicillin_ever   = 'Penicillin',
    cephalG1_ever     = 'Cephalosporin 1st',
    cephalG2_ever     = 'Cephalosporin 2nd',
    cephalG3_ever     = 'Cephalosporin 3rd',
    cephalG4_ever     = 'Cephalosporin 4th',
    macroclide_ever   = 'Macrolide',
    tetra_ever        = 'Tetracycline',
    quinolone_ever    = 'Quinolone',
    amino_ever        = 'Aminoglycoside',
    sulfon_ever       = 'Sulfonamide',
    carbapenem_ever   = 'Carbapenem',
    lincomycin_ever   = 'Lincomycin',
    polypep_ever      = 'Polypep',
    vancomycin_ever   = 'Vancomycin',
    tbdrug_ever       = 'TB drugs',
    antifungal_ever   = 'Antifungal',
    antiviral_ever    = 'Antiviral',
    antimalaria_ever  = 'Antimalarial',
    parasitedrug_ever = 'Parasite drugs',
    otheranti_ever    = 'Others'
  ) %>% 
  zap_labels()

vars <- append(names(sort_var(df, UnDiabetes:UnThalassemia)),'UnOth')
t2t_un <- create_tt(df, vars, FALSE)
t2s_un <- create_ts2(df, vars)
t2_un  <- tbl_merge(list(t2t_un, t2s_un), tab_spanner = FALSE)

vars <- names(select(df, UnSmoke:UnAlcohol, HIV, Covid21))
t2t_risk <- create_tt(df, vars, FALSE)
t2s_risk <- create_ts2(df, vars)
t2_risk  <- tbl_merge(list(t2t_risk, t2s_risk), tab_spanner = FALSE)

vars <- names(select(df, NP, CB))
t2t_pui <- create_tt(df, vars, FALSE)
t2s_pui <- create_ts2(df, vars)
t2_pui  <- tbl_merge(list(t2t_pui, t2s_pui), tab_spanner = FALSE)

vars <- append(names(sort_var(df, DxFever:DxMening)), 'DxOther')
t2t_dx <- create_tt(df, vars, FALSE)
t2s_dx <- create_ts2(df, vars)
t2_dx  <- tbl_merge(list(t2t_dx, t2s_dx), tab_spanner = FALSE)

vars <- names(select(df, SOFA1:SOFA6, Sofa_Sepsis))
t2t_or <- create_tt(df, vars, FALSE)
t2s_or <- create_ts2(df, vars)
t2_or  <- tbl_merge(list(t2t_or, t2s_or), tab_spanner = FALSE)

vars <- names(select(df, OxyInbu, vasopressor, oxygensupp, Hypoglycemia))
t2t  <- create_tt(df, vars)
t2s  <- create_ts(df, vars)
t2   <- tbl_merge(list(t2t, t2s), tab_spanner = FALSE)

vars <- names(select(df, CulBlood_ever:CulOther_ever))
t2t_cul <- create_tt(df, vars, FALSE)
t2s_cul <- create_ts2(df, vars)
t2_cul  <- tbl_merge(list(t2t_cul, t2s_cul), tab_spanner = FALSE)

vars <- names(sort_var(
      df,
      covid19_r:denguel_r,
      HBsAgr,
      HBc,
      AntiHBs,
      AntiHCV,
      hbshcv_r,
      Influenza,
      Leptor,
      MalariaR,
      Melio,
      scrubt_r,
      RSV
  )
)
t2t_rdt <- create_tt(df, vars, FALSE)
t2s_rdt <- create_ts2(df, vars)
t2_rdt  <- tbl_merge(list(t2t_rdt, t2s_rdt), tab_spanner = FALSE)

vars <- append(names(sort_var(df, penicillin_ever:parasitedrug_ever)), 'otheranti_ever')
t2t_trt <- create_tt(df, vars, FALSE)
t2s_trt <- create_ts2(df, vars)
t2_trt  <- tbl_merge(list(t2t_trt, t2s_trt), tab_spanner = FALSE)

t2 <- tbl_stack(list(t2_un, t2_risk, t2_pui, t2_dx, t2_or, t2, t2_cul, t2_rdt, t2_trt),
                group_header = c('Underlying Condition/Co-morbidity, n (%)',
                                 'Risk Behavior, n (%)',
                                 'PUI (SARS-CoV2 NGS and TAC), n (%)',
                                 'Provisional Diagnosis, n (%)',
                                 'Organ Dysfunction, n (%)',
                                 '',
                                 'Microbiology: Culture Source, n (%)',
                                 'RDT, n (%)',
                                 'Treatment (received), n (%)')) %>%
  format_table() %>%
  tab_style(style = cell_borders(sides = "bottom", style = "hidden"),
            locations = cells_row_groups(groups = 6))
t2
```

<br>

\newpage

**Table 3**: Microbiological blood culture results and common bacterial pathogens causing of sepsis
<br>
```{r t3}
df <- df_ipd %>%
  select(
    sepsis,
    dead28c,
    gramneg,
    achromobacter:vibrio,
    grampos,
    dermacoccus:streptococcus_su,
    gramneg_m,
    achromobacter_m:vibrio_m,
    grampos_m,
    dermacoccus_m:streptococcus_su_m
  ) %>%
  zap_labels()

varsneg <- names(sort_var(df, achromobacter:vibrio))
varspos <- names(sort_var(df, dermacoccus:streptococcus_su))
vars <- c('gramneg', varsneg, 'grampos', varspos)
t3t_all  <- create_tt(df, vars, FALSE, 'All')
t3a_all  <- create_t3(df_ipd, dead28c, vars)
t3b_all  <- create_t3(df_ipd, sepsis, vars)
t3ab_all <- tbl_merge(list(t3a_all, t3b_all), tab_spanner = c("**Mortality**", "**Sepsis Determination**"))
t3_all  <- tbl_merge(list(t3t_all, t3ab_all), tab_spanner = FALSE) %>% 
  format_table() 
t3_all

varsneg <- names(sort_var(df, achromobacter_m:vibrio_m))
varspos <- names(sort_var(df, dermacoccus_m:streptococcus_su_m))
vars <- c('gramneg_m', varsneg, 'grampos_m', varspos)
t3t_mdr  <- create_tt(df, vars, FALSE, 'MDR')
t3a_mdr  <- create_t3(df_ipd, dead28c, vars)
t3b_mdr  <- create_t3(df_ipd, sepsis, vars)
t3ab_mdr <- tbl_merge(list(t3a_mdr, t3b_mdr), tab_spanner = c("**Mortality**", "**Sepsis Determination**"))
t3_mdr  <- tbl_merge(list(t3t_mdr, t3ab_mdr), tab_spanner = FALSE) %>% 
  format_table() 
t3_mdr
```

<br>

\newpage

**Table 4**: Bivariate analysis discharge outcome of patient with sepsis activities at Nakhon Phanom and Mae Sot hospitals during November 2021- July 8, 2022 (N=`r n_ipd`)

```{r t4}
df <- df_ipd %>%
  mutate(across(Principal1:Principal3, ~ na_if(., "")),
         Others = ifelse(
           !is.na(Principal1) | !is.na(Principal2) | !is.na(Principal3),
           1,
           0
         )) %>%
  select(
    sepsis,
    dead28c,
    Pneumonia:Malaria,
    Others,
    DischargeStatus,
    DischargeType,
    TotalCharge
  ) %>%
  set_variable_labels(DischargeStatus = 'Discharge status',
                      DischargeType   = 'Discharge type ') %>%
  zap_labels()

vars <- append(names(sort_var(df, Pneumonia:Malaria)), 'Others')
t4t_dx <- create_tt(df, vars, FALSE)
t4s_dx <- create_ts2(df, vars)
t4_dx  <- tbl_merge(list(t4t_dx, t4s_dx), tab_spanner = FALSE)

vars <- names(select(df, DischargeStatus, DischargeType, TotalCharge))
t4t <- create_tt(df, vars)
t4s <- create_ts(df, vars)
t4  <- tbl_merge(list(t4t, t4s), tab_spanner = FALSE)

t4 <- tbl_stack(list(t4_dx, t4),
                group_header = c('Principal diagnosis, n (%)', '')) %>%
  format_table() %>%
  tab_style(style = cell_borders(sides = "bottom", style = "hidden"),
            locations = cells_row_groups(groups = 2))
t4
```
